---
title: "Comp/Stat 112: Spatial Visualization"
author: "Assignment 4 Solutions"
output:
  bookdown::html_document2:
    split_by: none
    toc: yes
    toc_depth: 3
    toc_float:
      toc_collapsed: true
    number_sections: false
---

```{r 05_setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
library(tidyverse)
library(ggplot2)
library(gplots)
library(maps) # for map data  #install.packages('maps')
library(ggmap) # for mapping points on maps  #install.packages('ggmap')
library(RColorBrewer) # for color palettes #install.packages('RColorBrewer')
library(leaflet) # for highly customizable mapping  #install.packages('leaflet')
library(ggthemes) # for more themes (including theme_map())  #install.packages('ggthemes')
library(usdata) #install.packages('usdata')
```


```{exercise}
In this exercise, you are going to create a single map of some of your favorite places! The end result will be one map.
```

a. Create a data set using the `tibble()` function that has 10-15 rows of your favorite places. The columns will be the name of the location, the latitude, the longitude, and a column that indicates if it is in your top 3 favorite locations or not. For an example of how to use `tibble()`, look at the `favorite_stp` that is created manually online.  

```{r}
#a)


```

b. Create a map that uses circles to indicate your favorite places. Label them with the name of the place. Choose the base map you like best. Color your 3 favorite places differently than the ones that are not in your top 3. Add a legend that explains what the colors mean. 

```{r}
#b)

```

c. Tell me about at least one of your favorite places. Why is it one of your favorite places (why is it special/important/fun to you)?


